Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-19 tex/MesnardoBarba2019.tex
Use PDF for line figures, PNG for filled contours
Add figure of spanwise-averaged vorticity

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.png}
    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
    \label{fig:osu_benchmarks}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.png}
    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
    \label{fig:poisson_benchmarks}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units fo flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$. Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
    \label{fig:vorticity2d}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.png}
    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
    \label{fig:force_coefficients}
\end{figure}

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.pdf}
    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
    \label{fig:osu_benchmarks}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.pdf}
    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
    \label{fig:poisson_benchmarks}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$. Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
    \label{fig:wz_2d}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/forceCoefficientsCompare2D.pdf}
    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack.}
    \label{fig:force_coefficients}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=7cm]{figures/wz_avg_multi_contourf.png}
    \caption{Filled contour of the spanwise-averaged z-component of the vorticity field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
    \label{fig:wz_avg_3d}
\end{figure}
